Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-15 paper/aldebaran.tex
WIP on data analysis section.

\begin{deluxetable}{lll}
\tablecolumns{3}
\tablecaption{\label{tab:parameters} The parameters in our model (see Eq.\ \eqref{eq:RV-model}).}
\tablehead{\colhead{Parameter} & \colhead{Prior} & \colhead{Description}}
\startdata
\cutinhead{Per-Site RV Offset and Uncertainty Scaling}
$\mu_j$ & $N\left[ \left\langle y_{j} \right\rangle, 10 \sigma_{y_{j}} \right] \left( \mu _j \right)\tablenotemark{a}$ & The per-site RV offset. \\
$\nu_j$ & $1/\nu_j, \quad \nu_j \in [1/2, 2]$ & The per-site uncertainty scale factor. \\
\cutinhead{Keplerian Parameters}
$K$ & $1/K, \quad K \in \left[ \min_j \sigma_{y_j}/100, \max_j 10 \sigma_{y_j} \right]$ & RV semi-amplitude. \\
$P$ & $1/P, \quad P \in [600, 700] \, \mathrm{d}$ & Keplerian period \\
$e$ & $2e$\tablenotemark{b} & Keplerian eccentricity \\
$\omega$ & $\mathrm{const}$ & Longitude of pericentre \\
$\chi$ & $\mathrm{const}$ & Pericentre passage is at $t = \chi P$\\
\enddata
\tablenotetext{a}{$\left\langle y_j \right\rangle$ and $\sigma_{y_j}$ are the mean and standard deviation of the RV timeseries from site $j$.}
\tablenotetext{b}{We actually sample in and impose a (flat) prior on $x \equiv e \cos \omega$ and $y \equiv e \sin \omega$.}
\end{deluxetable}

>>>>

\begin{deluxetable}{lll}
\tablecolumns{3}
\tablecaption{\label{tab:parameters} The parameters in our model (see Eq.\ \eqref{eq:RV-model}).}
\tablehead{\colhead{Parameter} & \colhead{Prior} & \colhead{Description}}
\startdata
\cutinhead{Per-Site RV Offset and Uncertainty Scaling}
$\mu_j$ & $N\left[ \left\langle y_{j} \right\rangle, 10 \sigma_{y_{j}} \right] \left( \mu _j \right)\tablenotemark{a}$ & The per-site RV offset. \\
$\nu_j$ & $1/\nu_j, \quad \nu_j \in [1/2, 2]$ & The per-site uncertainty scale factor. \\
\cutinhead{Keplerian Parameters}
$K$ & $1/K, \quad K \in \left[ \min_j \sigma_{y_j}/100, \max_j 10 \sigma_{y_j} \right]$ & RV semi-amplitude. \\
$P$ & $1/P, \quad P \in [600, 700] \, \mathrm{d}$ & Keplerian period \\
$e$ & $2e,\quad 0 \leq e < 1$\tablenotemark{b} & Keplerian eccentricity \\
$\omega$ & $\mathrm{const}, \quad 0 \leq \omega < 2\pi$ & Longitude of pericentre \\
$\chi$ & $\mathrm{const}, \quad 0 \leq \chi < 1$ & Pericentre passage is at $t = \chi P$\\
\enddata
\tablenotetext{a}{$\left\langle y_j \right\rangle$ and $\sigma_{y_j}$ are the mean and standard deviation of the RV timeseries from site $j$.}
\tablenotetext{b}{We actually sample in and impose a (flat) prior on $x \equiv e \cos \omega$ and $y \equiv e \sin \omega$.}
\end{deluxetable}
